Paper Six Summary

### 2015-10-27 hw/read/6/summary.tex
Added two possible improvements

\section*{Possible Improvements}
\begin{itemize}
\item In the Results section, some of the graphs are hard to read because they have been scaled down to fit on the page. Look at Figures 5 and 7 for example. The y-axis label runs into the labels along the y-axis. To fix this, the individual graphs should be split so that there is only one per column, or they should be combined and made bigger.
\end{itemize}

>>>>

\section*{Possible Improvements}
\begin{itemize}
\item In the Results section, some of the graphs are hard to read because they have been scaled down to fit on the page. Look at Figures 5 and 7 for example. The y-axis label runs into the labels along the y-axis. To fix this, the individual graphs should be split so that there is only one per column, or they should be combined and made bigger.
\item The authors could have reported the importance of their features in predicting defects using a measurement such as entropy. This could aid other researchers when selecting features.
\item The data mining methods used to extract features are summarized generally. The process can actual be very complex and depend on many assumptions. A specific and more detailed explanation could be more useful for future research.
\end{itemize}
